\plaintitle

### 2016-09-21 drafts/labor/decomposition.tex

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\onlyinsubfile{
  \usepackage{xr-hyper}
  \usepackage{hyperref}
}

\begin{document}

@@

\topic{As the additional context necessary to complete a task diminishes, the invisible labor of \textit{finding} tasks~\cite{martin2014being} has arisen as a major issue.}
\citeauthor{taskSearch} illustrate the task search challenges on AMT.%
Workers seek out good requesters~\cite{martin2014being} and then  ``streak'' to perform many tasks of that same type~\cite{taskSearch}.
%, and some work has gone into ameliorating the problems specific to this work site (\textit{ReLauncher}), % does anyone care for project names?
%while other work designs tasks around gap time (\textit{Twitch Crowdsourcing} \& \textit{Wait--Learning}) \cite{taskSearch,KucherbaevReLauncher,Vaish:2014:TCC:2611222.2556996,       Cai:2015:WLW:2702123.2702267}.
% \topic{One of the emergent properties of micro--tasks has been the relative cost of
%     \textit{finding} worthwhile tasks.}
%     The research community has documented and to some extent attempted to intervene in
%     the discovery of worthwhile tasks
%     \cite{taskSearch}.
Researchers have reacted by designing task recommendation systems (e.g.,~\cite{Cosley:2007:SUI:1216295.1216309})
%attempts to address this by directing workers to tasks through ``intelligent task routing'' \cite{Cosley:2007:SUI:1216295.1216309}.
and others focused on minimizing the amount of time that people need to spend doing anything other than the work for which they are paid~\cite{callison2014crowd}.

\subsubsection{\pieceworkpers}
\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{17} century%
, when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to compute astronomical phenomena
\cite{grier2013computers}.
%These workers became the first \textit{computers}.

The work that Airy solicited resonates with modern crowd work for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values%
, and have other workers check their work.
Second, tasks were discrete --- that is, independent from one another.
Finally, knowledge of the full scope of the project
--- indeed, knowledge of anything more than the problem set at hand ---
was unnecessary.

@@

>>>>

\documentclass[trackingWork]{subfiles}
% \makeatletter
% \def\blx@maxline{77}
% \makeatother
\onlyinsubfile{\usepackage{xr-hyper}
\usepackage{hyperref}
\externaldocument{complexity}
\externaldocument{relationships}
\externaldocument{decomposition}
}
\begin{document}

@@

\topic{As the additional context necessary to complete a task diminishes, the invisible labor of \textit{finding} tasks~\cite{martin2014being} has arisen as a major issue.}
\citeauthor{taskSearch} illustrate the task search challenges on AMT.%
Workers seek out good requesters~\cite{martin2014being} and then  ``streak'' to perform many tasks of that same type~\cite{taskSearch}.
%, and some work has gone into ameliorating the problems specific to this work site (\textit{ReLauncher}), % does anyone care for project names?
%while other work designs tasks around gap time (\textit{Twitch Crowdsourcing} \& \textit{Wait--Learning}) \cite{taskSearch,KucherbaevReLauncher,Vaish:2014:TCC:2611222.2556996,       Cai:2015:WLW:2702123.2702267}.

% \topic{One of the emergent properties of micro--tasks has been the relative cost of
%     \textit{finding} worthwhile tasks.}
%     The research community has documented and to some extent attempted to intervene in
%     the discovery of worthwhile tasks
%     \cite{taskSearch}.
Researchers have reacted by designing task recommendation systems (e.g.,~\cite{Cosley:2007:SUI:1216295.1216309})
%attempts to address this by directing workers to tasks through ``intelligent task routing'' \cite{Cosley:2007:SUI:1216295.1216309}.
and others focused on minimizing the amount of time that people need to spend doing anything other than the work for which they are paid~\cite{callison2014crowd}.

\subsubsection{\pieceworkpers}
\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{19} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to compute astronomical phenomena
\cite{grier2013computers}.
%These workers became the first \textit{computers}.

The work that Airy solicited resonates with modern crowd work for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values,
and have other workers check their work.
Second, tasks were discrete --- that is, independent from one another.
Finally, knowledge of the full scope of the project
--- indeed, knowledge of anything more than the problem set at hand ---
was unnecessary.

@@

\topic{Piecework researchers enumerate a number of problems with the decomposition of work, and the conflicting pressures managers and workers put forth.}
\citeauthor{bewley1999wages} in particular points out that
the approach of paying workers by the piece is
``\dots~not practical for workers doing many tasks, because of
the cost of establishing the rates and because
piecework does not compensate workers for time spent switching tasks''.
Ultimately, \citeauthor{bewley1999wages} argues that
``[piecework is] infeasible, because \dots
total output is the joint product of varying groups of people''
\cite{bewley1999wages}.
